Capstone Movielens Report

### 2025-12-07 reports/capstone-movielens.site/02.7.UMGYE-model.Rmd
UMGYE Model: Support Functions: section removed.

### UMGYE Model: Support Functions
\

::: {.noteblock data-latex=""}
Some of the functions described in this section accepts the `lambda` parameter, which we will need later for the _Model Regularization_ method. We use the [mean_reg](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L63) function call as well, which we will also need for the *Regularization* techniques to apply to our models (for details, see the  [mean_reg](#func.mean_reg) function description in the [Common Helper Functions: Regularization](#appndx_a.CHF.regularization) section of [Appendix A: Support Functions]).
We have already explained that in the [UME Model Regularization] section. 
For now, we omit the `lambda` parameter, accepting its default value `lambda = 0`. Let's recall that in this case, the [mean_reg](#func.mean_reg) function is equivalent to the standard R function [base::mean](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/mean).
:::

#### [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) Function {#func.calc_UMGY_effect_MSE}
\

The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.

##### Arguments
\

  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
  - **UMGY_effect:** A data structure returned by any of the following functions described above:
    - [calc_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

##### Source Code
\

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_MSE <- function(test_set, UMGY_effect){
  test_set |>
    left_join(edx.user_effect, by = "userId") |>
    left_join(rglr.UM_effect, by = "movieId") |>
    left_join(rglr.UMG_effect, by = "movieId") |>
    left_join(date_days_map, by = "timestamp") |>
    left_join(UMGY_effect, by='year') |>
    mutate(resid = rating - clamp(mu + a + b + g + ye)) |> 
    pull(resid) |> mse()
}
```

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_MSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L92) script. 
:::

#### [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) Function {#func.calc_UMGY_effect_MSE.cv}
\

The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.

##### Arguments
\

The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:

  - [calc_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

##### Source Code
\

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_MSE.cv <- function(UMGY_effect){
  start <- put_start_date()
  UMGY_effect_MSEs <- sapply(edx_CV, function(cv_fold_dat){
    cv_fold_dat$validation_set |> calc_UMGY_effect_MSE(UMGY_effect)
  })
  put_end_date(start)
  put_log1("Function: calc_UMGY_effect_MSE.cv
Date (Year) Effect MSE values have been computed for the %1-Fold Cross Validation samples.", 
           CVFolds_N)

  mean(UMGY_effect_MSEs)
}

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_MSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L102) script. 
:::

#### [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) Function {#func.calc_UMGY_effect_RMSE}
\

The function calculates the _Mean Squared Error (MSE)_ of the _UMGYE Model_ for the given _Test Set_ passed in the `test_set` parameter.

##### Arguments
\

  - **test_set:** A _Test Set_ dataset used for _UMGYE Model_ validation;
  - **UMGY_effect:** A data structure returned by any of the following functions described above:
    - [calc_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect](#func.train_UMGY_effect);
    - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

##### Source Code
\

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE <- function(test_set, UMGY_effect){
  mse <- test_set |> calc_UMGY_effect_MSE(UMGY_effect)
  sqrt(mse)
}
```

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_RMSE](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L114) script. 
:::

#### [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) Function {#func.calc_UMGY_effect_RMSE.cv}
\

The function calculates the _5-Fold Cross Validation MSE_ result for the _UMGY Effect_ data passed in the `UMGY_effect` parameter.

##### Arguments
\

The function accepts the only parameter: `UMGY_effect`, which is a data structure returned by the one of the following functions described above:

  - [calc_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect](#func.train_UMGY_effect);
  - [train_UMGY_effect.cv](#func.train_UMGY_effect.cv).

##### Source Code
\

The source code of the function is provided below:
```{r eval=FALSE}
calc_UMGY_effect_RMSE.cv <- function(UMGY_effect){
  UMGY_effect_RMSE <- sqrt(calc_UMGY_effect_MSE.cv(UMGY_effect))
  put_log2("%1-Fold Cross Validation ultimate RMSE: %2", 
           CVFolds_N, 
           UMGY_effect_RMSE)

  UMGY_effect_RMSE
}
```

::: {.noteblock data-latex=""}
The source code of the function [calc_UMGY_effect_RMSE.cv](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) is also available in the [UMGYE Model Support Functions](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/UMGY-effect.functions.R#L118) script. 
:::

@@

>>>>

@@

::: {.noteblock data-latex=""}
In the code snippets above, we use the [RMSEs.AddRow](#func.RMSEs.AddRow) and [RMSE_kable](#func.RMSE_kable) functions described in the [Result RMSEs Tibble Functions] section of [Appendix A: Support Functions].
:::
